---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# libminer

<!-- badges: start -->
[![R-CMD-check](https://github.com/agneke/libminer/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/agneke/libminer/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

libminer helps you understand the R package libraries installed on your
machine: how many packages you have, how much space they take up, and when
you installed them.

## Installation

You can install the development version of libminer from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("agneke/libminer")
```

## Example

`lib_summary()` counts (and optionally sizes) the packages in each of your
library paths:

```{r example}
library(libminer)

lib_summary()
lib_summary(sizes = TRUE)
```

`lib_starburst()` turns that summary into a colorful starburst plot, with one
wedge per library:

```{r starburst}
lib_starburst()
```

`lib_timeline()` shows *when* you installed each package, using the
modification time of each package's `DESCRIPTION` file as its install date —
handy for spotting bursts of installation activity (a new course, a new
project) versus quiet stretches:

```{r timeline}
lib_timeline()
```
